Untitled

### 2022-12-08 draft_report.Rmd
Update draft_report.Rmd

gigamuga_results <- list()
for (ind in ind_gm) {
  print(ind)
  sample_gm_res <- sample_haplotype_reconstruction('MURGIGV01', ind, samples_gen = T, qtl2_file_gen = T)
  gigamuga_results[[ind]] <- sample_gm_res
}
```

@@

```{r}
### MiniMUGA pipeline
minimuga_url <- 'http://haploqa-dev.jax.org/tag/MiniMUGA.html'
url_domain <- 'http://haploqa-dev.jax.org/'
marker_type <- 'MiniMUGA'
html_table <- read_html(minimuga_url) %>% html_nodes("a") %>% html_attr("href")
url_list <- paste0(url_domain, html_table[grepl('/sample', html_table)])
summary_df <- sample_summary_scrape(read_html(minimuga_url), url_list, marker_type)
ind_mini <- summary_df[summary_df$`Haplotype Candidate` == 'False',]$`ID`
ind_mini <- ind_mini[ind_mini!='JXX'] # screentime error, skip this one
ind_mini <- ind_mini[ind_mini!='JY9'] # only 1 contributing strain, AIL incompatible, skip this one as well
ind_mini <- ind_mini[ind_mini!='JY6'] # temporary - JXU, JY3, JY5
minimuga_results <- list()
mini_pct_res <- list()
for (ind in ind_mini) {
  #ind <- 'JXN'
  print(ind)
  sample_mini_res <- sample_haplotype_reconstruction('MiniMUGA', ind, samples_gen = F, qtl2_file_gen = F)

  df <- minimuga_geno_comp(sample_mini_res, ind, 'MiniMUGA')

@@

##### 3.2. Quantitative comparisons
Combining the results of the truth model, the qtl2 haplot
(Display the csvs, and perhaps the visualizations here too)

@@

# DO
do_pct_df <- fread(file.path(shiny_pct_fp, 'do_truth_comp.csv'))
do_pct_df
```

```{r}
# CC
cc_pct_df <- fread(file.path(shiny_pct_fp, 'cc_truth_comp.csv'))
cc_pct_df
#cc_pct_df
#ggplot(cc_pct_df) + aes(x = qtl2_pct_diff, y = haploqa_pct_diff) + geom_point()
```

```{r}
# BXD f3
bxd_pct_df <- fread(file.path(shiny_pct_fp, 'bxd_truth_comp.csv'))
bxd_pct_df

```{r}
# BXD f3
f2_pct_df <- fread(file.path(shiny_pct_fp, 'f2_truth_comp.csv'))
f2_pct_df

@@

MiniMUGA

@@

#### 4. Conclusion - TBD
Overall, the existing results for qtl2 genail and haploqa show that the two methods have very similar performance for most of the crosses, with genail performing significantly better for the DO outbred mice samples. HaploQA handles the extra founders being present in the haplotype reconstruction process better, however, qtl2 genail model has stronger capabilities to produce more accurate results for complicated crosses. So based on the results we have so far, we’re leaning toward that genail is more accurate than haploqa.

>>>>

gigamuga_results <- list()
gm_pct_res <- list()
for (ind in ind_gm) {
  print(ind)
  sample_gm_res <- sample_haplotype_reconstruction('MURGIGV01', ind, samples_gen = T, qtl2_file_gen = T)
  df <- minimuga_geno_comp(gigamuga_results[[ind]], ind, 'MURGIGV01')

  gm_pct_res[[ind]] <- df
  gigamuga_results[[ind]] <- sample_gm_res
}
```

@@

```{r}
### MiniMUGA pipeline
minimuga_url <- 'http://haploqa-dev.jax.org/tag/MiniMUGA.html'
url_domain <- 'http://haploqa-dev.jax.org/'
marker_type <- 'MiniMUGA'
html_table <- read_html(minimuga_url) %>% html_nodes("a") %>% html_attr("href")
url_list <- paste0(url_domain, html_table[grepl('/sample', html_table)])
summary_df <- sample_summary_scrape(read_html(minimuga_url), url_list, marker_type)
ind_mini <- summary_df[summary_df$`Haplotype Candidate` == 'False',]$`ID`
ind_mini <- ind_mini[ind_mini!='JXX'] # screentime error, skip this one
ind_mini <- ind_mini[ind_mini!='JY9'] # only 1 contributing strain, AIL incompatible, skip this one as well
ind_mini <- ind_mini[ind_mini!='JY6'] # temporary - JXU, JY3, JY5
minimuga_results <- list()
mini_pct_res <- list()
for (ind in ind_mini) {
  #ind <- 'JXN'
  print(ind)
  sample_mini_res <- sample_haplotype_reconstruction('MiniMUGA', ind, samples_gen = F, qtl2_file_gen = F)
  df <- minimuga_geno_comp(sample_mini_res, ind, 'MiniMUGA')

@@

##### 3.2. Quantitative comparisons

For visualizations, we constructed boxplots that demonstrate the percentage of marker that do not have the same results between qtl2, haploQA and the truth model:

@@

# DO
do_pct_df <- fread(file.path(shiny_pct_fp, 'do_truth_comp.csv'))
# CC
cc_pct_df <- fread(file.path(shiny_pct_fp, 'cc_truth_comp.csv'))
# BXD f3
bxd_pct_df <- fread(file.path(shiny_pct_fp, 'bxd_truth_comp.csv'))
# f2
f2_pct_df <- fread(file.path(shiny_pct_fp, 'f2_truth_comp.csv'))
```

@@

The two mutant mice crosses, GigaMUGA Mutant and MiniMUGA, do not have a tailored optimal model. Therefore, plotting the percentage of marker discordance between qtl2 genail and haploQA.

MiniMUGA:

@@

GigaMUGA mutant:

```{r}
gm_pct_temp <- rbindlist(gm_pct_res)
gm_plot <- gm_pct_temp %>% group_by(sample_id) %>% summarise(qtl2_pct_diff = sum(haplo_diplotype != qtl2_calls)/n()) %>% as.data.frame()
plot_df <- melt(gm_plot)
plot_df$variable <- 'GigaMUGA Mutant'

ggplot(plot_df) + geom_boxplot(aes(x = variable, y = value)) + ggtitle('GigaMUGA Mutant - percentage of marker difference between genail and haploqa') + xlab('model')

#### 4. Conclusion
Overall, the existing results for qtl2 genail and haploqa show that the two methods have very similar performance for most of the crosses, with genail performing significantly better for the DO outbred mice samples. HaploQA handles the extra founders being present in the haplotype reconstruction process better, however, qtl2 genail model has stronger capabilities to produce more accurate results for complicated crosses. So based on the results we have so far, we’re leaning toward that genail is more accurate than haploqa.
